### 2022-02-07 chapters/sctld/article.tex
last chapter added to manuscript

%% --- LIMITATION AND POTENTIAL IMPROVEMENTS OF THE MODEL --- %%
% 1. Limitations of hydro
As with any modeling study, it is important to understand the assumptions on which the model is based. Here, we have used a 2D barotropic ocean model forced by the 3D model HYCOM \citep{Chassignet2007} in order to indirectly represent baroclinic phenomena. Such a model is well-suited to simulate the fate of neutrally-buoyant material in shallow regions. However, as depth-averaged currents do not accurately approximate the motion of particles in the bottom and surface layers, they have been modified to simulate the exchanges of negatively and positively buoyant material. In order to derive bottom and surface currents from mean barotropic currents, we used parameterizations consistent with both observations and theory \citep{ardhuin2009observation,perlin2007organization, kundu1976ekman, smith2009influence}. Although such parametric estimation of surface and bottom currents adds additional uncertainty to those simulations, using a 2D model as the basis for the study allowed for reef-scale resolution throughout the whole FRT with available computational resources. Such high-resolution allowed the simulation to explicitly represent recirculation eddies around islands and reefs, that significantly impact the weighted connectivity length as well as the local retention of pathogenic material on the reefs \citep{frys20}.

>>>>

%% --- LIMITATION AND POTENTIAL IMPROVEMENTS OF THE MODEL --- %%
% 1. Limitations of hydro
As with any modeling study, it is important to understand the assumptions on which the model is based. Here, we have used a 2D barotropic ocean model forced by the 3D model HYCOM \citep{chassignet2007hycom} in order to indirectly represent baroclinic phenomena. Such a model is well-suited to simulate the fate of neutrally-buoyant material in shallow regions. However, as depth-averaged currents do not accurately approximate the motion of particles in the bottom and surface layers, they have been modified to simulate the exchanges of negatively and positively buoyant material. In order to derive bottom and surface currents from mean barotropic currents, we used parameterizations consistent with both observations and theory \citep{ardhuin2009observation,perlin2007organization, kundu1976ekman, smith2009influence}. Although such parametric estimation of surface and bottom currents adds additional uncertainty to those simulations, using a 2D model as the basis for the study allowed for reef-scale resolution throughout the whole FRT with available computational resources. Such high-resolution allowed the simulation to explicitly represent recirculation eddies around islands and reefs, that significantly impact the weighted connectivity length as well as the local retention of pathogenic material on the reefs \citep{frys20}.

### 2022-02-07 chapters/sctld/sctld.tex
last chapter added to manuscript

\item \textbf{T. Dobbelaere}, E. M. Muller, L. J. Gramer, D. M. Holstein, $\&$ E. Hanert, 2020, Coupled Epidemio-Hydrodynamic Modeling to Understand the Spread of a Deadly Coral Disease in Florida, \textit{Frontiers in Marine Science},69: 1121-1132. \href{https://www.frontiersin.org/article/10.3389/fmars.2020.591881 }{doi: 10.3389/fmars.2020.591881}
\end{list}

>>>>

\item \textbf{Dobbelaere, T.}, Muller, E. M., Gramer, L. J., Holstein, D. M., $\&$ Hanert, E. (2020). Coupled epidemio-hydrodynamic modeling to understand the spread of a deadly coral disease in Florida. \textit{Frontiers in Marine Science},1016. \href{https://www.sciencedirect.com/science/article/pii/S1463500322000026}{doi: 10.3389/fmars.2020.591881}.
\end{list}

### 2022-02-07 thesis.tex
slim+swan paper added
chapter on drto added to thesis
last chapter added to manuscript

\newcommand{\hycom}{\textsc{hycom} }
\newcommand{\ie}{\textit{i.e}} 
\newcommand{\eg}{\textit{e.g.}}

\begin{document}
\frontmatter
  \input{include/title}
  \clearemptydoublepage
  \input{include/abstract}
  %\clearemptydoublepage
  \input{include/thanks}
  \clearemptydoublepage
  \tableofcontents
  \clearemptydoublepage
  % \input{include/glossary}
  % \clearemptydoublepage
  \mainmatter 
%%%%
\mychapter{Introduction} \label{chap:intro}
 \input{chapters/intro/intro}    
%%
%%%%%% 
  \mychapter{Modeling the spread of SCTLD in Florida} \label{chap:sctld}
  \chaptermark{Modeling the spread of SCTLD in Florida}  
  \input{chapters/sctld/sctld}
%%
% \mychapter{Paper Dry Tortugas} \label{chap:ontario}
% \chaptermark{Paper DRTO}  
%   \input{chapters/ontario/ontario}
%
% \mychapter{Paper onset} \label{chap:eigenmode}
% \chaptermark{Paper onset}  
%   \input{chapters/eigenmode/eigenmode}
%%%   
%%%%%%%%%%%
%
%%%%%  
%%%
  \mychapter{Conclusions and perspectives} \label{chap:conclusion}
  \input{chapters/conclusions/conclusions}    
%%
%
  \clearemptydoublepage
  \bibliography{include/bibliography.bib}

>>>>

\begin{document}
\frontmatter
  \input{include/title}
  \clearemptydoublepage
  \input{include/abstract}
  %\clearemptydoublepage
  \input{include/thanks}
  \clearemptydoublepage
  \tableofcontents
  \clearemptydoublepage
  % \input{include/glossary}
  % \clearemptydoublepage
  \mainmatter 
%%%%
\mychapter{Introduction} \label{chap:intro}
 \input{chapters/intro/intro}    
%%
%%%%%% 
\mychapter{Modeling the spread of SCTLD in Florida} \label{chap:sctld}
\chaptermark{Modeling the spread of SCTLD in Florida}  
\input{chapters/sctld/sctld}
\mychapter{Transmission of SCTLD from the Marquesas to the Dry Tortugas}\label{chap:drto}
\chaptermark{Transmission of SCTLD from the Marquesas to the DRTO}  
\input{chapters/drto/drto}
\mychapter{The onset of the SCTLD outbreak and the PortMiami Deep Dredge Project} \label{chap:onset}
\chaptermark{Onset of SCTLD and PortMiami Deep Dredge Project}  
\input{chapters/onset/onset}
\mychapter{Impacts of hurricanes on wave-induced ocean transport processes} \label{chap:irma}
\chaptermark{Wave-induced transport under hurricanes}  
\input{chapters/irma/irma}
%%%%%%%%%%%
%
%%%%%  
%%%
  \mychapter{Conclusions and perspectives} \label{chap:conclusion}
  \input{chapters/conclusions/conclusions}    
%%
%
  \clearemptydoublepage
  \bibliography{include/bibliography.bib}
